### 2009-11-11 docs/marcello-dissertation/thesis/chapter2.tex
Bugs in the bibtex file were preventing the references to be printed.
This revision also carries the format submitted by Niki
 - preamble and sfsuthesis format

git-svn-id: svn://localhost/netbeams/branches/marcello/persistence@636 559edde2-a4d4-44e0-96fc-4035e40d7396

%\bibliography{thesis}  % uses the references stored in Chapter1Radar.bib

@@

As it is shown, the data produced by this type of sensor runs in the order of
at most hundreds of Megabytes a year, what can be considered a very low data
storage requirement. Upon collecting the data from sensors, the RTC lab staff
use automation scripts written in Matlab to process, index and distribute the
raw data in different formats, including the OPeNDAP \ref{opendap}, a format
widely used in the research institutions that promotes easier data exchange
among them.

@@

The Data Sensor Platform, in short DSP Platform, is based on a micro-kernel
architecture developed on top of the Java modular framework called OSGi
\ref{osgi}. The platform represents the foundation of the execution of
NetBEAMS, since it is executed from an embedded hardware called Gumstix
\ref{gumstix} using a Linux operating system and on top of the Java Virtual
Machine (JVM). In order to transport data from sensors hosts to the network
sink, the use of a cellular connection is used to transport the collected data
from the senso devices using the HTTP Protocol, as described by
\cite{netbeams09}. Figure \ref{fig:sf-netbeams-node} shows the
architecture of the inhanced node designed by the NetBEAMS research group.

>>>>

\bibliography{thesis}  % uses the references stored in Chapter1Radar.bib

@@

As it is shown, the data produced by this type of sensor runs in the order of
at most hundreds of Megabytes a year, what can be considered a very low data
storage requirement. Upon collecting the data from sensors, the RTC lab staff
use automation scripts written in Matlab to process, index and distribute the
raw data in different formats, including the OPeNDAP \cite{opendap}, a format
widely used in the research institutions that promotes easier data exchange
among them.

@@

The Data Sensor Platform, in short DSP Platform, is based on a micro-kernel
architecture developed on top of the Java modular framework called OSGi
\cite{osgi}. The platform represents the foundation of the execution of
NetBEAMS, since it is executed from an embedded hardware called Gumstix
\cite{gumstix} using a Linux operating system and on top of the Java Virtual
Machine (JVM). In order to transport data from sensors hosts to the network
sink, the use of a cellular connection is used to transport the collected data
from the senso devices using the HTTP Protocol, as described by
\cite{netbeams2009}. Figure \ref{fig:sf-netbeams-node} shows the
architecture of the inhanced node designed by the NetBEAMS research group.

### 2009-11-11 docs/marcello-dissertation/thesis/preamble.tex
* This revision fixes the problem related to the table of contents that was not printed.   - The package for hiper-link is responsible for the bug in the preamble.tex.
* References to the misc should be done by using \ref instead of \cite.

* Renaming a few bibliographic entries.

git-svn-id: svn://localhost/netbeams/branches/marcello/persistence@635 559edde2-a4d4-44e0-96fc-4035e40d7396
Bugs in the bibtex file were preventing the references to be printed.
This revision also carries the format submitted by Niki
 - preamble and sfsuthesis format

git-svn-id: svn://localhost/netbeams/branches/mar

\documentclass[12pt,oneside]{sfsuthesis}

\usepackage{amsthm,amsmath,amssymb,amsfonts,latexsym,graphicx,enumerate,setspace,verbatim,tocloft}

%\usepackage{color}                    % For creating colored text and background
%\usepackage{hyperref}                 % For creating hyperlinks in cross references
% other possibly useful packages: textcomp,mathrsfs,amscd,epsfig,euscript,cancel

@@

\hoffset=.5in 
\oddsidemargin=0in   % = 1in because LaTeX adds 1in
\evensidemargin=0in  % = 1in because LaTeX adds 1in
\topmargin=0in       % = 1in because LaTeX adds 1in
\headheight=0in
\headsep=1in         % Distance from top of pagenum (for page numbers at top-right corner of page) to text
\footskip=1.2in      % Distance from bottom of text to the page number (for page number at bottom of page)
\textwidth=5.9in     % Should be 6in, but use 5.9in to be conservative
\textheight=8.0in    % Best for Title Page (will change after the Title Page)

@@

\usepackage[latin1]{inputenc}
\usepackage[USenglish]{babel}
\usepackage[dvips]{hyperref}

@@

\[ \]
\vspace{-1.9in}

@@

\singlespace{A thesis presented to the faculty of\\
San Francisco State University\\
In partial fulfilment of\\
The requirements for\\ The degree}

@@

\vspace{3.1in}

@@

\newpage
\textheight=7.1in    % For all pages after the Title Page -- try making this number smaller (7.0 or 6.9) if the bottom margins are too small
\footskip=1.1in      % Distance from bottom of text to the page number (for page number at bottom of page)
\thispagestyle{empty}

@@

\newpage
\thispagestyle{empty}
\[ \]
\vspace{-1.8in}
\begin{center}
{CERTIFICATION OF APPROVAL}
\end{center}
\vspace{.6in}
\begin{quote}
I certify that I have read {\it \mytitle} by \myname and that in my opinion this work meets the criteria for approving a thesis submitted in partial fulfillment of the requirements for the degree: Master of Science in Computer Science at San Francisco State University.
\end{quote}

\vspace{0.75in}

@@

\hrule{\hspace{3.5in}} \\ 
Prof. Arno Puder, Ph.D.\\
Professor of Computer Science\\

\vspace{1in}

\hrule{\hspace{3.5in}} \\
Prof. Marguerite C. Murphy, Ph.D.\\
Professor of Computer Science

@@

\singlespace{
\myname \\
San Francisco State University \\ 
\thisyear \\
}

@@

\vspace{.3in}

\doublespacing{\noindent
Your abstract comes here. % maximum one page
}

@@

\vspace{.6in}

\hrule{\hspace{3.75in}} \\[-10pt]
Chair, Thesis Committee 
\hspace{2.5in}
Date

\newpage
\[ \]
\vspace{-1.8in}
\begin{center}{ACKNOWLEDGMENTS}\end{center}

\vspace{.3in}
\begin{quote}
\noindent
I thank everybody and their mothers\dots (optional).
\end{quote}

\renewcommand{\contentsname}{\vspace{-1.8in} \begin{center} \normalsize \rm TABLE OF CONTENTS \end{center}}
\renewcommand{\listfigurename}{\vspace{-1.8in} \begin{center} \normalsize \rm LIST OF FIGURES \end{center}}
\renewcommand{\listtablename}{\vspace{-1.8in} \begin{center} \normalsize \rm LIST OF TABLES \end{center}}
\renewcommand{\cftchapfont}{\normalfont}
\renewcommand{\cftchappagefont}{\normalfont}
\renewcommand{\cftchapleader}{\cftdotfill{\cftdotsep}} % formatting commands for table of contents
\renewcommand{\cftsecfont}{\normalfont}
\renewcommand{\cftsecpagefont}{\normalfont}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}

>>>>

\documentclass[12pt,oneside]{sfsuthesis}
\usepackage{amsthm,amsmath,amssymb,amsfonts,latexsym,graphicx,enumerate,setspace,verbatim,makeidx,subfigure, multirow, url, soul}
\usepackage[subfigure]{tocloft}
\usepackage{color}                       % For creating colored text and background
%\usepackage{hyperref}                 % For creating hyperlinks in cross
%references
% other possibly useful packages: textcomp,mathrsfs,amscd,epsfig,euscript,cancel

@@

\hoffset=.5in 
\oddsidemargin=0in
\evensidemargin=0in
\topmargin=0.1in 
\headheight=0in
\headsep=1in
\footskip=.8in
\textwidth=5.9in
\textheight=7in

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

@@

\usepackage[latin1]{inputenc}
\usepackage[USenglish]{babel}

@@

\[ \]
\vspace{-1.8in}

@@

\singlespace{A thesis presented to the faculty of\\
San Francisco State University\\
In partial fulfillment of\\
The requirements for\\ The degree}

@@

@@

\newpage
\thispagestyle{empty}

@@

\newpage
\thispagestyle{empty}
\[ \]
\vspace{-1.8in}
\begin{center}
{CERTIFICATION OF APPROVAL}
\end{center}
\vspace{.5in}
\begin{quote}
I certify that I have read {\it \mytitle} by \myname, and that in my opinion this work meets the criteria for approving a thesis submitted in partial fulfillment of the requirements for the degree: Master of Science in Computer Science at San Francisco State University.
\end{quote}

\vspace{1.5in}

@@

\hrule{\hspace{3.5in}} \\ 
Prof. Arno Puder, Ph.D.\\
Professor of Computer Science\\
\vspace{1in}
\hrule{\hspace{3.5in}} \\
Prof. Marguerite C. Murphy, Ph.D.\\
Professor of Computer Science

@@

\singlespace{
\myname \\
San Francisco, California \\  
\thisyear \\
}

@@

%\doublespacing{\noindent
\onehalfspacing{\noindent      
Abstract goes here
}

@@

\hrule{\hspace{3.75in}} \\[-10pt]
Chair, Thesis Committee 
\hspace{2.5in}
Date
\doublespacing
\newpage
\[ \]
\vspace{-1.8in}
\begin{center}{ACKNOWLEDGMENTS}\end{center}

\vspace{.5in}
\begin{quote}
\noindent
Acknowledgments
\end{quote}

\renewcommand{\contentsname}{\vspace{-1.7in} \begin{center} \normalsize \rm TABLE OF CONTENTS \end{center}}
\renewcommand{\listfigurename}{\vspace{-1.7in} \begin{center} \normalsize \rm LIST OF FIGURES \end{center}}
\renewcommand{\listtablename}{\vspace{-1.7in} \begin{center} \normalsize \rm LIST OF TABLES \end{center}}
\renewcommand{\cftchapfont}{\normalfont}
\renewcommand{\cftchappagefont}{\normalfont}
\renewcommand{\cftchapleader}{\cftdotfill{\cftdotsep}} % formatting commands for table of contents
\renewcommand{\cftsecfont}{\normalfont}
\renewcommand{\cftsecpagefont}{\normalfont}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
